### 2016-11-25 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Eds
EDITS BEFORE DRAFT TO DAVE

table1A <- data.frame(Model = apply(t1,1,getterms,c(2:10)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(table1A) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(table1A) <- NULL
table1A$Model[table1A$Model == ''] <- 'Null model'
table1A[,3:5] <- lapply(table1A[,3:5],as.numeric)

@@

table1B <- data.frame(Model = apply(t1,1,getterms,c(2:8)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(table1B) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(table1B) <- NULL
table1B$Model[table1B$Model == ''] <- 'Null model'
table1B[,3:5] <- lapply(table1B[,3:5],as.numeric)

#Sort out rounding and exlcude NAs from blank spaces. Clunky but works
table1 <- rbind(c('A',rep(' ',4)),table1A,c('--',rep(' ',4)),c('B',rep(' ',4)),table1B)
table1[,3:5] <- lapply(table1[,3:5],as.numeric)
table1[,3:5] <- round(table1[,3:5],3)
table1[,3:5] <- lapply(table1[,3:5],as.character)
table1[is.na(table1)] <- " "

@@

>>>>

table1A <- data.frame(Model = apply(t1,1,getterms,c(2:10)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(table1A) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(table1A) <- NULL
table1A$Model[table1A$Model == ''] <- 'Null model'
table1A[,3:5] <- lapply(table1A[,3:5],as.numeric)
table1A[,3:5] <- round(table1A[,3:5],3)

@@

table1B <- data.frame(Model = apply(t1,1,getterms,c(2:8)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(table1B) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(table1B) <- NULL
table1B$Model[table1B$Model == ''] <- 'Null model'
table1B[,3:5] <- lapply(table1B[,3:5],as.numeric)
table1B[,3:5] <- round(table1B[,3:5],3)

#Sort out rounding and exlcude NAs from blank spaces. Clunky but works
table1 <- rbind(c('A',rep('-',4)),table1A,c('B',rep('-',4)),table1B)

@@

RTL_Full2 <- standardize(RTL_Full)
